The relative roles of genetic, ecological and environmental factors in species radiations

### 2017-11-02 paper/draft.tex
extend new angle for intro (stub)

Because the study of islands biogeography takes into account evolutionary time frames (millions of years),
comprehensive and meaningful data is difficult to obtain.
In a recent review \cite{leidinger2017biodiversity}, we analyzed a powerful alternative to field experiments in island biogeography
--- mechanistic (/simulation) models.
Unfortunately, most island models failed to include more explicit genetic or micro evolution.
Instead some models featured a concept known as ``protracted speciaton'' \cite{rosindellXXX}, where speciation occurs with a delay from the actual
divergence event if the population remains isolated during that time.

>>>>

Because the study of islands biogeography takes into account evolutionary time frames (millions of years),
comprehensive and meaningful data is difficult to obtain.
In a recent review \cite{leidinger2017biodiversity}, we analyzed a powerful alternative to field experiments in island biogeography
--- mechanistic (/simulation) models.
Unfortunately, most island models failed to include more explicit genetic or micro evolution.
Instead some models featured a concept known as ``protracted speciaton'' \cite{rosindellXXX}, where speciation occurs with a delay from the actual
divergence event if the population remains isolated during that time.
But nature is usually more complex than this and genetic mechanisms have important ramifications for speciation/radiation and species richness.
[EXAMPLES!]

Another shortfall of the reviewd models was the lack of integrating ecological niches and adaption.

In the following, we present a model that remedies both of the adressed shortcomings by implementing genetic processes on a niche-explicit background
in an island biogeography framework.
We will adress the questions of what relative impact does (a) genetic linkage and (b) reproductive isolation have on emerging species numbers and diversity,
(c) what ...
We find that
